Molecular dynamics simulation of synchronization in driven particles

### 2021-01-18 manuscript/manuscript_ajp_2020.tex
slight edits to conclusion, added notes in table 1 about experimental values (see tex doc)

\begin{table}[h!]
\centering
\caption{Simulation units and approximate values
  in experiment. (coming soon!)}
\begin{ruledtabular}
\begin{tabular}{c c c } %p{5cm}}
Quantity & Simulation Unit & Experimental range\\
\hline
length &  $a_0 = 1$ & $ < a_0 <$\\
energy & $E_0 = 1$ & $ < E_0 <$ \\
%electric potential & $V(r_{ij}) = E_0/r_{ij}$ \\
%energy & $E_0 = q^2{Z^*}^2/4\pi \epsilon \epsilon_0 a_0$ \\
%dimensionless interaction strength & $q$ \\
%effective colloidal charge & $Z^*$ \\
%solvent dielectric constant & $\epsilon \epsilon_0$\\
force & $F_0 = E_0 / a_0$ & $<F_0<$\\
velocity &  $ a_0 / \tau $ &  $ < v < $\\
viscosity coefficient & $\eta = F_0 \tau / a_0 $ & $ <\eta<$\\
time &  $ \tau = \eta a_0 / F_0 $ & $ < \tau <$\\

@@

\section{Conclusion}
\label{sec:conclusion}	% You can label sections for reference
Fundamental models
of synchronization 
can include many coupled oscillators
or focus on 
a single particle driven across a periodic potential landscape.
Single particle studies 
are useful to understand synchronization
in the absence of collective effects.
%A single particle particle oscillator
%within a potential well is 
%much like a skateboarder in a half-pipe or
%a child on a swing
%moving back and forth. % through equilibrium.  % \cite{}.
The relationship between the driving force and
landscape can change the pattern of motion.  
With a constant or 
dc drive the landscape modulates 
the particle velocity, below some threshold  
the dc force is not strong enough to push the particle
across a potential maximum so the average velocity is zero,
a phenomena referred to as pinning \cite{Reichhardt2017}.  
%and dissipating energy from the system at all driving forces.
A sinusoidal or ac drive creates mode-locking,
where the average particle velocity
is fixed for a range of dc drive forces \cite{Reichhardt2015}.

Our simulations reproduce results presented in 
Juniper {\it et al.} \cite{Juniper2015, Juniper2018}
which demonstrated
mode locking in
experiments and simulations of 
driven colloids on a
optical periodic landscape.
Due to the relative ease of
manipulation and imagining, 
colloids are used as experimental models
for systems relatively hard to access and visualize. 
%SAME SENTENCE TWICE
Collections of colloids can
be used to study the properties of solids and liquids
%comprised of smaller particles
%such as atoms \cite{} or electrons \cite{}
or more exotic systems 
such as cold atoms or electron gases \cite{Grier2003}.

%Oscillators ordered into chains or lattices.
%has many important
%technological applications
Dynamical mode-locking
is %often
observed
in quantum electronic
devices such as Josephson junctions \cite{Josephson1962,Josephson1965}.
A single junction contains 
two superconductoring layers which sandwich an insulating layer.
When subject to an external voltage,
Cooper pairs in the superconducting materials
tunnel through the insulating layer.
Phase-locking is observed as 
%phase-locked current loops \cite{} 
stepped regions in current-voltage (I-V) relationship in these devices,
where voltage is the analog of external driving force
and current is that of particle velocity.
%where a constant current results from a range of voltages
%due to the quantized nature of the tunneling probability [NOT QUITE RIGHT...].
%instead of ohmic relationships.
Known as Shapiro steps, % \cite{},
these phase locked currents  
have been observed due to applied ac voltages in 
single Josephson junctions \cite{Shapiro1963, Golubov2004} and
coupled arrays of junctions \cite{Benz1990}.
%either in 
%velocity-force curves and voltage-current curves \cite{Golubov2004}.
Shapiro steps vary in width depending on the strength of the
applied ac forces,
and are observed in a variety of systems
displaying
%are hallmarks of
non-Ohmic behavior in voltage-current curves,
including
ac and dc driven
charge and spin density waves.

%where these steps are generated
%by the tendency of the response of a system
%to be flat across a range of applied driving forces or voltages,
%which can be probed with
%  atoms on surfaces.
%  voltage driven superconducting vortices
%  confined in a Josephson junction,

%
%
%mini review of synchronization in electronics
%careful - the following is all simulations
%Recent studies demonstrate
%that coupled electronic oscillators can be
%programmed for use as micro-controllers for robotic locomotion \cite{Dutta2019}.

@@

  We acknowledge Harvey Gould and Jan Tobochnik,
  who invited us to write the article and
  supported its development.
  Charles and Cynthia Reichhardt advised 
  the project and provided the original molecular dynamics code
  written in the C programming language.
  We acknowledge funding from the M.J. Murdock Charitable Trust
  and the Pacific Research Institute for Science and Mathematics (PRISM).

>>>>

\begin{table}[h!]
\centering
\caption{Simulation units and approximate values
  in experiment ~\cite{Juniper2015}.
{\it might be more appropriate to match Juniper parameters more precisely given our focus...}}
\begin{ruledtabular}
\begin{tabular}{c c c } %p{5cm}}
Quantity & Simulation Unit & Experimental range\\
\hline
length &  $a_0 = 1$ & $ a_0 \sim 1.5 \mu m$\\
energy & $E_0 = 1$ & $ < E_0 <$ \\
%electric potential & $V(r_{ij}) = E_0/r_{ij}$ \\
%energy & $E_0 = q^2{Z^*}^2/4\pi \epsilon \epsilon_0 a_0$ \\
%dimensionless interaction strength & $q$ \\
%effective colloidal charge & $Z^*$ \\
%solvent dielectric constant & $\epsilon \epsilon_0$\\
force & $F_0 = E_0 / a_0$ & $<F_0<$\\
velocity &  $ a_0 / \tau $ &  $ < v < $\\
viscosity coefficient & $\eta = F_0 \tau / a_0 $ & $ <\eta<$\\
%juniper uses water–ethanol mixture
time &  $ \tau = \eta a_0 / F_0 $ & $ < \tau <$\\

%FROM JUNIPER2015
%l¼3.5 mm and a laser power per trap of WE0.75mW (trap stiffness: k=3.8\times10^7 kg /s^2; trap depth: V0 = 75 k_B T
%ref51
%Juniper, M. P. N., Besseling, R., Aarts, D. G. A. L. & Dullens, R. P. A. Acousto- optically generated potential energy landscapes: potential mapping using colloids under flow. Opt. Express 27, 28707–28716 (2012).
%U(x) measured in ratio of k_BT from -75 to -25
%0 < vAC < 8 micrometer/s and frequency f=0.25 to 0.75 Hz.
%0 < vDC < 5 micrometer/s
%convert to force units?
%check when steps exist - in Juniper - steps don't exist for n=1or n=3, even though steps exist for n¼0,2,4,5 and 6.
%flexible chains
%dipole interaction $\Gamma \propto B^2$
%\Gamma =15 (B=0.43mT) and a stiff chain at \Gamma=392 (B=2.2mT).
%Kink
%16 particles in a strong potential energy landscape of 15 minima (trap spacing: l¼5.5 mm; laser power per trap: WE1.75 mW; trap stiffness: k¼8.7?10?7 kg s?2; trap depth: V0¼200 kBT),

%Volpe AJP Parameters
%We will consider a silica microparticle in water with radius R=1micro m, mass m=11picograms, viscosity eta=0.001 Ns/m^2; $\gamma=6\pi \eta R$,  T=300K, and \tau=0.6\micro s.

@@

\section{Conclusion}
\label{sec:conclusion}	% You can label sections for reference
%Fundamental models
%of synchronization 
%can %include many coupled oscillators
%or
%focus on 
A single particle driven across a periodic potential landscape 
%Single particle studies are useful
to understand synchronization
in the absence of collective effects
due to interactions between particles.
%A single particle particle oscillator
%within a potential well is 
%much like a skateboarder in a half-pipe or
%a child on a swing
%moving back and forth. % through equilibrium.  % \cite{}.
The relationship between the driving force and
landscape can change the pattern of motion.  
With a constant or 
dc drive the landscape modulates 
the particle velocity, below some threshold  
the dc force is not strong enough to push the particle
across a potential maximum so the average velocity is zero,
a phenomena referred to as pinning \cite{Reichhardt2017}.  
%and dissipating energy from the system at all driving forces.
A sinusoidal or ac drive creates mode-locking,
where the average particle velocity
is fixed for a range of dc drive forces \cite{Reichhardt2015}.
Our simulations reproduce results presented in 
Juniper {\it et al.} \cite{Juniper2015, Juniper2018}
which demonstrated
mode locking in
experiments and simulations of 
driven colloids on a
optical periodic landscape.
Due to the relative ease of
manipulation and imagining, 
colloids are used as experimental models
for systems relatively hard to access and visualize. 
%SAME SENTENCE TWICE

Collections of colloids can
be used to study the properties of solids and liquids
%comprised of smaller particles
%such as atoms \cite{} or electrons \cite{}
or more exotic systems 
such as cold atoms or electron gases \cite{Grier2003}.
%Oscillators ordered into chains or lattices.
%has many important
%technological applications
Dynamical mode-locking
is %often
observed
in quantum electronic
devices such as Josephson junctions \cite{Josephson1962,Josephson1965}.
A single junction contains 
two superconductoring layers which sandwich an insulating layer.
When subject to an external voltage,
Cooper pairs in the superconducting materials
tunnel through the insulating layer.
Phase-locking is observed as 
%phase-locked current loops \cite{} 
stepped regions in current-voltage (I-V) relationship in these devices,
where voltage is the analog of external driving force
and current is that of particle velocity.
%where a constant current results from a range of voltages
%due to the quantized nature of the tunneling probability [NOT QUITE RIGHT...].
%instead of ohmic relationships.
Known as Shapiro steps, % \cite{},
these phase locked currents  
have been observed due to applied ac voltages in 
single Josephson junctions \cite{Shapiro1963, Golubov2004} and
coupled arrays of junctions \cite{Benz1990}.
%either in 
%velocity-force curves and voltage-current curves \cite{Golubov2004}.
Shapiro steps vary in width depending on the strength of the
applied ac forces,
and are observed in a variety of systems
displaying
%are hallmarks of
non-Ohmic behavior in voltage-current curves,
including
ac and dc driven
charge and spin density waves
and superconducting vortices in landscapes 
engineered with periodic patterns of pinning sites.
Our results can be relevant 
to synchronization effects
in a broad range of experiments systems
including optically confined colloids,
superconductors with periodic pinning arrays, 
and the charge and spin of atomic systems.

%where these steps are generated
%by the tendency of the response of a system
%to be flat across a range of applied driving forces or voltages,
%which can be probed with
%  atoms on surfaces.
%  voltage driven superconducting vortices
%  confined in a Josephson junction,
%mini review of synchronization in electronics
%careful - the following is all simulations
%Recent studies demonstrate
%that coupled electronic oscillators can be
%programmed for use as micro-controllers for robotic locomotion \cite{Dutta2019}.

@@

  We acknowledge Harvey Gould and Jan Tobochnik,
  who invited us to write the article and
  supported its development.
  Charles and Cynthia Reichhardt advised 
  the project and provided the original molecular dynamics code
  written in the C programming language.
  We acknowledge funding from the M.J. Murdock Charitable Trust
  and the Pacific Research Institute for Science and Mathematics. % (PRISM).
